---
title: "New York Airbnb hotel dashboard"

output: 
  flexdashboard::flex_dashboard:
    source_code: embed
    vertical_layout: scroll
    theme: yeti
    orientation: column

---


Please check out rpub link for better version of this dashboard.

Rpubs give better design compare to kaggle kernel for Rmarkdown and Rscript.

.

http://rpubs.com/billynguyen/nyairbnbdashboard



``` {js}
// Inverse color of navigation bar.
$('.navbar-inverse').removeClass('navbar-inverse').addClass('navbar-default');
```

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse) # metapackage with lots of helpful functions
library(caret)
library(highcharter)
library(ggmap)
library(leaflet)
library(plotly)
library(DT)
library(shiny)
list.files(path = "~/Documents/BigDataAnalytics/final_project")
df <- read.csv("~/Documents/BigDataAnalytics/final_project/new-york-city-airbnb-open-data/AB_NYC_2019.csv")
```


```{r, include=FALSE}
df$reviews_per_month[is.na(df$reviews_per_month)] <- 0
df <- df %>% mutate(avg_price = price/minimum_nights)
```

Overview
=======================================================================

 Column {.tabset .tabset-fade data-width=700 .colored }
-----------------------------------------------------------------------

### Location
```{r, fig.height=7}
leaflet(df %>% select(longitude,neighbourhood_group,neighbourhood,latitude,price)) %>%
  setView(lng = -73.95, lat = 40.73,zoom = 10) %>%
   addTiles() %>% 
  addMarkers(
  clusterOptions = markerClusterOptions())
```

Column {data-width=300}
-----------------------------------------------------------------------

### Number of hotel
```{r, fig.height=0.25}
valueBox(nrow(df), icon = "fa-ship", color="rgb(100,100,100)")
```

### Average price per day
```{r, fig.height=0.25}
valueBox(round(mean(df$price, na.rm = T),0), icon = "fa-heart", color="rgb(200,100,100)")
```


### Price by neighbourhood group
```{r,fig.height=2}
ggplotly(
  df %>% 
    filter(!(abs(avg_price - median(avg_price)) > 2*sd(avg_price))) %>%
    ggplot(aes(neighbourhood_group, avg_price, fill = neighbourhood_group)) +
    geom_boxplot() + 
    labs(title = "Average price by neighbourhood group",
         x = "neighbourhood", y = "average price per day ($)") +
    theme_classic() + theme(legend.position = "none")
)
```


### Price by room type
```{r,fig.height=2}
ggplotly(
  df %>% 
    filter(!(abs(avg_price - median(avg_price)) > 2*sd(avg_price))) %>%
    ggplot(aes(room_type, avg_price, fill = room_type)) +
    geom_boxplot() + 
    labs(title = "Average price by room type",
         x = "room type", y = "average price per day ($)") +
    theme_classic() + theme(legend.position = "none")
)
```

Room type
=======================================================================

 Column {data-width=700 .colored }
-----------------------------------------------------------------------

### Average price per day of common room
```{r, fig.height=2.5}
hchart(df$avg_price, color = "#B71C1C", name = "Price per day") %>%
  hc_title(text = "Average price of all room") %>%
  hc_add_theme(hc_theme_ffx())
```

### Average price per day of high-class room
```{r,fig.height=2.5}
hchart(df$avg_price[df$avg_price > 500], color = "#006699", name = "Price per day") %>%
  hc_title(text = "Average price of high-class room") %>%
  hc_add_theme(hc_theme_ffx())
```

Column {data-width=300}
-----------------------------------------------------------------------

### Number of common rooms
```{r,fig.height=0.25}
valueBox(nrow(df %>% 
                filter(avg_price < 500)), icon = "fa-heart",color="#B71C1C")
```


### Average price per day of common rooms
```{r, fig.height=0.25}
valueBox(round(mean(df$avg_price[df$avg_price < 500]),0), icon = "fa-heart",color="#B71C1C")
```

### Number of high-class room
```{r, fig.height=0.25}
valueBox(nrow(df %>% 
                filter(avg_price >= 500)), icon = "fa-heart",color="#006699")
```

### Average price per day of high-class rooms
```{r, fig.height=0.25}
valueBox(round(mean(df$avg_price[df$avg_price >= 500]),0), icon = "fa-heart",color="#006699")
```

### Availability
```{r,fig.height=3}
hchart(df$availability_365, color = "#336666", name = "Availability") %>%
  hc_title(text = "Overall room availability") %>%
  hc_add_theme(hc_theme_ffx())
```


